### 2016-05-04 pubs/hcar16/hcar16.tex
some minor edit to paper

Our approach is similar to that of the
\href{https://dl.acm.org/citation.cfm?id=2503779}{Intel
  Labs Haskell Research Compiler}: to use GHC as a front-end to generate STG
(or Core), then exit to our own back-end compiler.  As in their case we do not
attempt to use the GHC runtime.  Our implementation is \emph{light-weight} in
that we are not attempting to support or recreate the vast functionality of
GHC and its runtime.  This approach is also similar to
\href{http://www.cse.unsw.edu.au/~pls/thesis/dons-thesis.ps.gz}{Don Stewart's}
except that we generate C instead of Java.

>>>>

Our approach is similar to that of the
\href{https://dl.acm.org/citation.cfm?id=2503779}{Intel Labs Haskell Research
  Compiler}: to use GHC as a front-end to generate STG (or Core), then exit to
our own back-end compiler that is itself written in Haskell.  As in their case
we do not attempt to use the GHC runtime.  Our implementation is
\emph{light-weight} in that we are not attempting to support or recreate the
vast functionality of GHC and its runtime.  This approach is also similar to
\href{http://www.cse.unsw.edu.au/~pls/thesis/dons-thesis.ps.gz}{Don Stewart's}
except that we generate C instead of Java.
